\documentclass{article}
\usepackage{fullpage}
\usepackage{longtable}
\begin{document}

\newcommand{\h}{\hspace*{4ex}}

% rend - tear / wrench violently
% litany, lament
% acquiesce - accept reluctantly without protest
% boorish - bad-manered/rough/course
%
%
% rending/pairing silence
%
%
% letting blood intertwine \\
% sanguinary pools at the bottom \\
% of a fountain with a broken pump \\
% staining stone carmine; red like clay \\
% depleating, never restored.

\begin{center}
\begin{longtable}{l}
\textbf{A Poem About Beef Wellington} \\
{\small\textbf{And abosolutely nothing else.}} \\
\\
Are you aware, that in a true Wellington, \\
the duxelles is mostly dirt? \\
\\
You remind me of a nice plump Wellington. \\
%and I don't mean the dish. \\
The sorry weasels that live in holes; \\
too scared to leave the ground. \\
They cake themselves in mud and muck \\
to keep them from being found. \\
\\
How does it feel to be a little log \\
with your entrails along your back? \\
So easy to pluck and rip your guts \\
as one deveins a shrimp? \\
\\
Evolution is ever so cruel, \\
you were always destined to be meat. \\
Dressed in dough and painted gold--- \\
My! what a glorious feast. \\
\\
Just like the Wellington, \\
Nothing gives you pulse to rise. \\
You drift in a listless sea. \\
For when the world wakes \\
you do not contend \\
but offer yourself as feed. \\
\\
Why would you saunter \\
out from your home \\
when all that exists is there? \\
Your contention is a trap and \\
your comfort a snare. \\
Why, when was the last \\
you breathed fresh air? \\
\\
How does it feel to be so alone? \\
To always rack yourself in fear? \\
Stagnation seems gracious \\
but its all so heinous--- \\
you could die if you tripped on the stairs. \\
\\
You and the Wellington--- \\
twins of dispair--- \\
a joke of the divine \\
and delicious beyond compare. \\

%To not sense the change in the air? \\
%Your stagnation is gracious for it hasn't \\
%let you in on the plan. \\
%\\
%But the heat wave is coming \\
%and my tummy's rumbling. \\
%So let's get the show on the road! \\
%Dress yourself in buttery dough \\
%and in the oven you go. \\
%As just like the Welly, \\
%you're a dying old breed \\
%better with bread than cheese. \\

%I know what you're thinking, but \\
%\h{}\h{}beef Wellington \\
%\h{}actually\h{}exists. \\
%\\
%Or at least the Wellington \\
%was not always beef. \\
%\\
%The Wellington was a weasel \\
%with its entrails exposed; \\
%a perfect log of meat and fat \\
%ripe to be rolled in dough. \\
%\\
%This weasel, you see, was a menace \\
%of sorts, always burrowing into the ground. \\
%The old old Duke had had enough \\
%and held a hound-wound hunt.
%\\
%And thus a creature once abound \\
%is now nowhere to be found. \\
\end{longtable}
\end{center}
\end{document}

