\documentclass{article}
\usepackage{fullpage}
\usepackage{longtable}
\begin{document}

\newcommand{\h}{\hspace*{4ex}}

\begin{center}
\textbf{...} \\
\vspace*{2ex}
\begin{longtable}{l}
Many are stricken by a plague that sits in their minds, \\
yet no one knows and no one cares about these demons \\
they invite inside. \\
\\
But I---after long meditation, \\
trial, and reflection--- \\
have devised a cure. \\
\\
You see, \\
If idle hands are the devil's playthings \\
then idle minds must be much more. \\
\\
And it is exactly this postulate \\
on which I have based my work. \\
\\
As the director of a sanitarium \\
I have recorderd the following symptoms \\
of which to be wary: \\
\h{}The fickle \\
\h{}The bashful \\
\h{}The bold \\
\h{}mild-to-severe acne \\
\h{}palpatations \\
\h{}epilepsy \\
\h{}stiff joints \\
\h{}poor posture \\
\h{}and a penchant for spicy foods. \\
\\
And so, it is with science and plainess \\
that I stand here to inform you that such \\
infirmities and their roots may be stricken \\
with an altered diet. \\
\\
Spice is a parlance in the ways of Asmodai \\
and must be expunged; thus to my merit \\
I have devised a new food \\
that I shall now introduce to you: \\
\\
When you're \\
choking the chicken at home alone \\
the devil has his way \\
and that's why we say \\
be sure to eat \\
a bland breakfast \\
every day \\
with Corn Flakes \\
get yourself some Corn Flakes \\
to shake the urge \\
to touch yourself \\
in service to Asmodai. \\
That's Corn Flakes \\
Kellogg's Corn Flakes \\
\\
unsweatened, puffed corn, cereal \\
\\
Thank you all for your time, \\
I shall leave you now in summary: \\
\\
Don't hold ya' meat \\
and don't flick the bean; \\
instead, grab a spoon! \\
Get a bowl! \\
And get some flakes! \\
They're all you'll ever need \\
to stay sin free. \\
\\
That's the Kellogg's Guarantee. \\
\end{longtable}
\end{center}
\end{document}

