\documentclass{article}
\usepackage{fullpage}
\usepackage{longtable}
\begin{document}

\newcommand{\h}{\hspace*{4ex}}

% I didn't really know where I was going with the "My Mind is a Nightmare"
% series until I drafted this piece.  I believe that, while the pieces are
% all very disconnected, the series shows a growth in my life from depression
% into something all together different.  There is a final piece for the set
% planned after this one and I hope the completion is everything I thought it
% could and would be.

\begin{center}
\textbf{To Love A Witch} \\ % Working Title
{\small\textbf{My Mind is a Nightmare, Part 3}} \\
\vspace*{2ex}
\begin{longtable}{l}
\multicolumn{1}{c}{\textbf{I.}} \\
I was always told to never cross a witch, \\
but no one told me to never love one either. \\
\\
\multicolumn{1}{c}{\textit{Lost in the woods at night,}} \\
\multicolumn{1}{c}{\textit{strange trees line the way;}} \\
\multicolumn{1}{c}{\textit{nauseating.}} \\
\multicolumn{1}{c}{\textit{As they claw at your frame}} \\
\multicolumn{1}{c}{\textit{a hut appears}} \\
\multicolumn{1}{c}{\textit{caked in mud, silt, and loam}} \\
\multicolumn{1}{c}{\textit{in a clearing}} \\
\multicolumn{1}{c}{\textit{where flowers cease to desist.}} \\
\\
\multicolumn{1}{c}{\textit{Their beauty draws you in.}} \\
\multicolumn{1}{c}{\textit{Lunacy of a red moon's light}} \\
\multicolumn{1}{c}{\textit{assailed by bats and bones}} \\
\multicolumn{1}{c}{\textit{you enter the Nekromant's home}} \\
\multicolumn{1}{c}{\textit{and partake of the cretin's stew.}} \\
\\
\multicolumn{1}{c}{\textit{Three sips; you taste the snake's tounge}} \\
\multicolumn{1}{c}{\textit{Valerian death fills your lungs}} \\
\multicolumn{1}{c}{\textit{and then you sleep.}} \\
\\
\multicolumn{1}{c}{\textit{All the while,}} \\
\multicolumn{1}{c}{\textit{the witch returns}} \\
\multicolumn{1}{c}{\textit{for her turn to eat.}} \\
\\
% Middle bits; need meeting up with appearance, young, but dishevaled
% This is the goat witch and that needs to be presented.
As it turns out, there was a shack in the woods \\
with long-worn walls, roughly maintained. \\
It sat amidst a garve-laiden garden; \\
each stone, nameless but not aimless. \\
They were meticulously placed North-bound headings \\
and their keeper: oaken-hair, pale, disheveled, \\
but careful. \\
\\
When I first met the witch \\
she was dumping out a pungent green liquid \\
that gurgled as it filled a freshly dug pit. \\
\h ``What's that?'' I asked. \\
``Souls,'' she replied, ``dirty, rotten souls. \\
Always fouling up the place.'' \\
\h ``And now fouling the Earth?'' \\
``And now to be cleansed and returned to the dirt.'' \\
% Originally I wanted the aforementioned souls to be a state of depression,
% the sad thoughts of the nearby villagers, however, I wasn't sure how to
% phrase it and instead it now appears to be a form of evil.  I'm okay with
% the change but I feel that it may overall weaken the piece from the original
% intent of having the goat witch take on the suffering of the people.
\\
She drew a soft silver liquid from her hand \\
into a nearby bucket. \\
As her breathing slowed and her eyes relaxed, \\
she whispered against the wind. \\
She poured out her soul; \\
shaking every last drop from the pail, \\
carefully, so as to avoid breaking \\
the rust-worn structure. \\
\\
\multicolumn{1}{c}{``Out in the woods} \\
\multicolumn{1}{c}{when the moon grows pale} \\
\multicolumn{1}{c}{the witch can be found} \\
\multicolumn{1}{c}{casting her spells} \\
\multicolumn{1}{c}{with spirit's fire} \\
\multicolumn{1}{c}{and stone-worn veils} \\
\multicolumn{1}{c}{for the world to prosper} \\
\multicolumn{1}{c}{and it's evil quelled.''} \\
% There's definitely a cadence to the above selection.  Here as a song sung by
% the witch.  I originally had a different version that was to be used earlier
% in the piece but then dropped it.  The purpose was to contrast how the people
% think of the witch's work with what the witch actually does.  The above
% version being the witch's which shows a positivity and her strive to make the
% world a better place at the cost of her self.
\\
She turned toward me, \\
the shadows casting her smile wry, \\
that I knew to be genuine. \\
\\
\multicolumn{1}{c}{\textbf{II.}} \\ % Pt. 2 y'all
I was always told that I would feel love one day, \\
but no one told me that butterflies appear in pairs. \\
\\
The first is weak, \\
a gentle hum nursing from a bud. \\
It tests its wings, gaining strength, \\
until it is ready for flight. \\
\\
The second, erratic; clipped wings \\
pumping harder to stay aloft. \\
Its flight is chaos, \\
inflamining imperfections, \\
turning my heart poignant. \\
\\
\multicolumn{1}{c}{\textit{Strigarum. Heretic.}} \\ % Stry-gare-um
\multicolumn{1}{c}{\textit{Sulpher tinctured in blood,}} \\
\multicolumn{1}{c}{\textit{the witch's kiss.}} \\
\multicolumn{1}{c}{\textit{Sanguinary bliss}} \\
\multicolumn{1}{c}{\textit{a murky wine}} \\
\multicolumn{1}{c}{\textit{evil's your tounge}} \\
\multicolumn{1}{c}{\textit{with her lies.}} \\
\\
\multicolumn{1}{c}{\textit{Strigarum. Sorcerer.}} \\
\multicolumn{1}{c}{\textit{Lust-befallen recourse}} \\
\multicolumn{1}{c}{\textit{for the one who turned your Faustus.}} \\
\multicolumn{1}{c}{\textit{In dusk we ride,}} \\
\multicolumn{1}{c}{\textit{torches high}} \\
\multicolumn{1}{c}{\textit{lighting the cross.}} \\
\\
\multicolumn{1}{c}{\textit{Sacrosanct now apostate.}} \\
\multicolumn{1}{c}{\textit{The witch will die tonight}} \\
\multicolumn{1}{c}{\textit{and the birds sing once more}} \\
\multicolumn{1}{c}{\textit{as you forget that whore.}} \\
\\
\end{longtable}
\end{center}
\end{document}

