\documentclass{article}
\usepackage{fullpage}
\usepackage{longtable}
\begin{document}

% Thank you Kat!

% averice / genial
% portant
% capacious
% vessil
% lilted
% vitriolic
% abhoring
% usurp

%
% INTJ if you want Myers Briggs but I find it shifting
% as I grow into something of a cacophony of all the different
% letters attempting to voice their opinions
%
% The biggest struggle loving myself...
% That'd be me and my stupid head.
% Shit gets weird in there.
% It's all agraid to love anythign and it constantly
% finds thigns wrong with other things so it doesn't have to get close to them.
%
% I joke about a lot of shit in poetry but I think the biggest theme
% ends up being like a duality and a duel between the two main
% influential "voices" in my head that I call the scholar and the beast.
% It's like a demon and an angel but they switch sides often because
% either one can be the lesser of my two evils.

%
% But dear, you're an ornament, an accessory to...
%

%
% Voided thought
%

%
% Fearing the silence, we scream
%

%
% Caterize and atone.
% Unioverse etched into your stone.
%

%
% like crows
%

% Sometimes you try to take pictures of something but they all come
% out blurry, like the person isn't really there at all.

\newcommand{\h}{\hspace*{2ex}}

\newcommand{\TC}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\TL}[1]{\multicolumn{1}{l}{#1}}
\newcommand{\TR}[1]{\multicolumn{1}{r}{#1}}


\begin{center}
\textbf{Inner Turmoil} \\
{\small\textbf{My Mind is a Nightmare, Part 2}} \\
\vspace*{2ex}
\begin{longtable}{c}
\TC{\textit{The Mind is its own place, and in itself}} \\
\TC{\textit{Can make a heav'n of hell, [and] a hell of heav'n.}} \\
\TC{\footnotesize{(\textit{Paradise Lost}, Book 1; John Milton)}} \\
\\
\TC{\textbf{I.}} \\
% Section 1 Text
\TC{The Scholar stands in front of you.} \\
\\
\TC{``Quizzle me this,'' it says,} \\ % Thanks to R.F. Daniels for this one.
\TC{``You dive into the river of Acheron,} \\
\TC{desperately searching for what you've lost} \\
\TC{as the hands try to pull you down.} \\
\TC{But you don't let them take you.} \\
\TC{Instead, you stay suspended mid-buoyancy} \\
\TC{in the hazy stillness that surrounds you.} \\
\\
\TC{How long can you survive submerged before drowning?''} \\
\\
Your smile fades and you avert your eyes \\
as the Scholar moves to your right. \\
\\
\TC{\textbf{II.}} \\
% Section 2 Text
\TC{The Beast stands before you.} \\
\TC{It leans it's snout up to your ear} \\
\TC{and whispers.} \\
\\
\TC{``The question is flawed.} \\
\TC{You are content.} \\
\TC{You place yourself into a box.} \\
\TC{You wander the necropolis within.} \\
\TC{You carve your words into sepulchers.} \\
\TC{You name them monuments.''} \\
\\
\TC{The Beast usurps the Scholar which falls to your left.} \\
\\
\TC{\textbf{III.}} \\
% Section 3 Text
\TC{The beast leans in once more,} \\
\TC{Now vitriolic} \\ % Now vitriolic and swollen
\TC{Now swollen\ \ } \\ % alignment spaces
\TC{its arm around your shoulders.} \\
\\
\TR{We are the dead.} \\
\TR{Our existances breathe hollow} \\
\TR{and bare no sweat.} \\
\TR{We are not echos} \\
\TR{and, thus, we will simply} \\
\TR{cease to exist.} \\
\\
\TC{It grins.} \\
\\
\TC{\textbf{IV.}} \\
% Section 4 Text
\TC{You are afraid of death.} \\       % Narrator
\TL{You are afraid of dying alone.} \\ % Scholar
\TC{You are afraid of loving} \\       % Narrator
\TC{yourself.} \\
\TR{You were not meant to love.} \\    % Beast
\TL{You are afraid of emotion.} \\     % Scholar
\TR{You are afraid of humanity,} \\    % Beast
\TR{yours or otherwise.} \\
\TC{But you are not worthless.} \\     % Narrator
\TC{You are not truely alone.} \\
\TC{You are simply lost in the cacophany} \\
\TC{of each letter you let define you,} \\
\TC{all voicing their opinions at once.} \\
\\
\TC{\textbf{V.}} \\
% Section 5 Text
\TC{You step forward,} \\
\TC{allowing the Scholar to castle the Beast.} \\
\\
\TR{``You are unfinished,'' the Scholar states.} \\
\TR{``Defined by ink still welled---''} \\
\\
\TL{``As time grows stale,'' interjects the Beast.} \\
\\
\TC{A single bell tolls in the distance, while,} \\
% 1st is the passing bell
% 2nd is the death knell
% 3rd is the lych/corpse bell
% Could just use bell tolling thrice?
\TC{once again} \\
\TC{the Beast and the Scholar change sides.} \\
% The scholar: "You are unfinished; defined by ink still welled."
\end{longtable}
\end{center}

\end{document}
