\documentclass{article}
\usepackage{fullpage}
\usepackage{longtable}
\begin{document}

\newcommand{\h}{\hspace*{4ex}}

\begin{center}
\textbf{Untitled} \\
\vspace*{2ex}
\begin{longtable}{l}
``GOOD MORNING I LOVE YOU'' \\
\\
The text comes all caps and mispelled. \\
You find this endearing \\
as you imagine her thinking of you \\
as her alarm snaps her awake \\
from a pleasant dream; the two of you \\
entwined and in sync \\
beating as one being. \\
The sudden jolt to consciousness \\
leaving her bittersweet \\
but wanton in her greeting, \\
so excited to wish your day well \\
that she could not contain herself \\
to correct her mistakes. \\
\\
For a moment uncertainty strikes you. \\
What if, in reality, \\
she just didn't care enough about you \\
to fix it. \\
\\
You linger in that moment, \\
unsure of how to respond. \\
After all, \\
she broke up with you last month \\
to date her best friend--- \\
a void you now fill--- \\
and while you weren't emotionally invested \\
at the time, \\
it still hurts the same. \\
\\
``I love you too! I hope you have a great day!'' \\
\\
This situation is not uncommon. \\
And your friends rightfully \\
insist that it is not okay. \\
You understand \\
but you do not care. \\
\\
Later in the week \\
she texts you from the bar. \\
Her anxiety has overcome her \\
and she wishes to go home. \\
She is unable to leave by herself \\
so you drive to meet her. \\
\\
She is not alone \\
her boyfriend is enjoying himself \\
among friends. \\
She does not wish to be rude \\
and so you join them. \\
\\
You are sociable and she is drunk. \\
You integrate but she remains an outcast. \\
\\
Her father texts her, \\
angry about---what you deam--\\
an avoidable situation. \\
This upsets her; \\
intensified by inebriation. \\
\\
In panic, she claims she will walk home \\
and leaves the bar. \\
\\
You glance at her boyfriend.
``Are you going to handle this, or should I?'' \\
There is bite to your words. \\
You are angry but you are unsure what for, \\
if toward him or toward her. \\
\\
The boyfriend returns, barely having left. \\
She will not speak to him. \\
\\
She is no where to be found outside. \\
You call, only to find her next door \\
taking refuge in a pizza parlor \\
from the cold. \\
\\
She refuses to go home without her car \\
so you drive her to \textit{his} apartment \\
where she gathers her things \\
leaving a breakup note \\
on an old pizza box \\
insisting that this is where \\
he is most sure to find it. \\
\\
You are weak to her words \\
and exhausted \\
so you let her drive, \\
but only in caravan. \\
\\
``You're an amazing person \\
and I am so thankful for you.'' \\
\\
The morning is unexpected as she elaborates. \\
\\
``I love you more than I do Danny Divito.'' \\
\\
You understand the sincerity, but still you hurt. \\
The next day she re-unites with her boyfriend. \\
\\
This story repeats itself in different forms \\
so many times you could call it a beat; \\
a lurid regurgitation swallowed back. \\
The burn lingers on your throat for days. \\
\\
You've always known you have a fetish for chaos \\
but you never want to admit it. \\
\\
``I thought when I met you that you \\
would be forgettable--- \\
\h{}a haze-cast night \\
\h{}on an otherwise short life--- \\
but instead you taught my holy \\
that it could be beaten. \\
That my conceit, \\
\h{}entertaining that date, \\
was a parley with fate \\
negotiating away my monotony. \\
I am sorry, but I still have feelings for you.'' \\
\\
``Oh'' she says flatly. \\
Her reation is unexpected as she elaborated. \\
``I assumed you didn't.'' \\
\\
You remain composed in your exhilaration \\
as you carry on as if this gives you life. \\
\\
\end{longtable}
\end{center}
\end{document}
