\documentclass{article}
\usepackage{fullpage}
\usepackage{longtable}
\begin{document}

\newcommand{\h}{\hspace*{4ex}}

% rend - tear / wrench violently
% litany, lament
% acquiesce - accept reluctantly without protest
% boorish - bad-manered/rough/course
%
%
% rending/pairing silence
%
%
% letting blood intertwine \\
% sanguinary pools at the bottom \\
% of a fountain with a broken pump \\
% staining stone carmine; red like clay \\
% depleating, never restored.

\begin{center}
\textbf{Untitled 13} \\ % Working Title
\vspace*{2ex}
\begin{longtable}{l}
To the cold gilded eye \\
\h{}he exists in twilight, \\
\h{}a corpuscular entity \\ % Corpuscular not Crepuscular!
\h{}lost to the world. \\
\\
He stands amidst a desert \\
\h{}straddling cracked islands, \\
\h{}questioning the stability \\
\h{}of something so broken. \\
\\
From his lament, \\
\h{}he bears three besotted imps, \\
\h{}feathered and beaked; \\
\h{}cawing abreast flesh made ossuary. \\
\\
\h{}Look, laugh, gawk at the boy \\
with the raven-courted crown \\
unaware how close \\
to the grave he stands. \\
\\
\h{}Caress his graying cheek, \\
kiss his rot, \\
and warm his touch \\
while sliding a knife across his gut. \\
\\
\h{}Carefully \\
remove his abdomen, \\
swing in his stomach, \\
and debauch his liver. \\
\\
\h{}Once sated, \\
hold his battered hands, \\
place thimbles on his tips, \\
but do not teach him to sew. \\
\\
\h{}Instead, \\
unspool your thread \\
into small knotted piles for him \\
to untangle before he can mend. \\
\\
The boy will forgive and forget \\
\h{}until the sun is a ghost; \\
\h{}a glass memory framed in gold \\
\h{}reflecting fresh wounds; \\
\\
Remaining in litany \\
\h{}flayed and stitched \\
\h{}flayed and stitched \\
\h{}flayed, unstitched. \\
\end{longtable}
\end{center}
\end{document}

