\documentclass{article}
\usepackage{fullpage}
\begin{document}
I found myself listless and lost under caramel skies as the sun set overhead
in an array that could only be described as the first bite of a
particularly sweet honeydew melon.
It was just me and my steering wheel getting more intimate than
a human should with an inanimate object covered with sticky, aging
vinyl that I prefer to refer to as pleather since the song my
nails played over the ribs and valleys was more Nickelback than
Johnny Cash.
\\
\\
I was ready to lean in for a kiss with my dirty old man,
a '98 Volkswagen Beetle that had likely seen better days,
when that house came into view.
\\ \\
\noindent
\begin{tabular}{l}
It was a brick house. \\
An ALL brick house. \\
It knew it had everything \\
that a house needs to give a family. \\
\end{tabular}
\\ \\
\noindent
900 by 800 square feet of salacious shale and clay
just waiting to be lived in.
\\
\\
The American dream.
\\
\\
I pulled into the spacious Hollywood driveway,
laying fresh tire over the new concrete.
I stretched my arms to the Southern Heat as I walked up
up, caressing the horizontal knob, giving it a full
93 degrees of torque; gently exposing the the maple
woodwork within.
\\
\\
I found my way to the bathroom after checking each
door in turn as I passed, touching everything I could
to take it all in.  The toilet formed a soft
whirlpool of yellow-brown molasses leading down
into a porcelain cave.
\\
\\
I wondered where those caves might lead
when I heart a call.
\\ \\
\indent ``Honey, whose car is that?'' \\
\\
I quickly set foot to tile, not stopping to sanitize my hands,
bolted for my car, hopped inside, and off into the evening I rode,
giving backwards glances every few feet so that the house
would know that I was still thinking about it.

\end{document}
